### 2013-01-26 mcmc.tex
outline and references

\section{Statistical error bars}

@@

\clearpage
\begin{thebibliography}{}\markright{References}

\bibitem[Bovy, Hogg, \& Roweis(2009)]{bovy}
  Bovy,~J., Hogg,~D.~W., \& Roweis, S.~T., 2009,
  Extreme deconvolution: inferring complete distribution functions from noisy, heterogeneous, and incomplete observations,
  \arxiv{0905.2979} [stat.ME]

\bibitem[Foreman-Mackey et al.(2012)]{emcee} Foreman-Mackey,
    D., Hogg, D.~W., Lang, D., \& Goodman, J.\ 2012, \arxiv{1202.3665}

\end{thebibliography}

>>>>

\section{When do you need MCMC?}

...Search, optimization, and sampling in inference.

\section{What is MCMC?}

\section{Metropolis--Hastings, stretch move, and more}

...M-H, emcee, and references to competitor methods like nested and hamiltionian etc.

\section{Results, error bars, and figures}

...using the output to make figures, get numbers with error bars, and show results

\section{Tuning}

...tuning and Gibbs sampling and the like

\section{Convergence}

...how do you know you have run long enough?

\section{Initialization and burn-in}

\section{Advice and discussion}

...Don'ts and no-nos and breaking Markov-ness.

@@

\clearpage
\begin{thebibliography}{}\markright{References}
\bibitem[Foreman-Mackey et al.(2012)]{emcee}
  Foreman-Mackey,~D., Hogg,~D.~W., Lang,~D., \& Goodman,~J.\ 2012,
  \project{emcee}: The MCMC Hammer,
  \arxiv{1202.3665}
\end{thebibliography}
